---
title: "Some Helpers"
author: "Jan-Philipp Kolb"
date: "17. April 2015"
output: slidy_presentation
---

## Update R

- installr package [here](http://www.r-statistics.com/2013/03/updating-r-from-r-on-windows-using-the-installr-package/) and 
[here](https://cran.r-project.org/web/packages/installr/installr.pdf)


```{r,eval=F}
# installing/loading the package:
if(!require(installr)) {
install.packages("installr"); require(installr)} #load / install+load installr
 
# using the package:
updateR() 
```

- [10 tipps to become a better coder](http://www.r-bloggers.com/10-top-tips-for-becoming-a-better-coder/)

## HTML and CSS

- [HTML & CSS](http://www.codecademy.com/tracks/web) 

- [Howto on CSS](http://www.w3schools.com/css/css_howto.asp)

<http://yihui.name/knitr/demo/engines/>

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css
        
        
You can enable figure captions by `fig_caption: yes` in YAML:        
        
```    
output:
      rmarkdown::html_vignette:
        fig_caption: yes        
```




## [Github](http://github.org) 

- Use [github with Rstudio](http://www.molecularecologist.com/2013/11/using-github-with-r-and-rstudio/)


## `knitr`

[knitr with other languages](http://shiny.rstudio.com/articles/css.html)


## rmarkdown

see the documentation for the rmarkdown package

```{r,eval=F}
library(rmarkdown)
```

- [A cheatsheet](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet#blockquotes) on the usage of Rmarkdown. 

- [Here](http://yihui.name/knitr/options/) you can find the chunk options.

- [More about knittr](http://yihui.name/knitr/demo/showcase/)

- [Here](http://www.unexpected-vortices.com/sw/rippledoc/quick-markdown-example.html) is how to embed formulas:

- If you need a [bibliography](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html). 

- If you want to write a [vignette](http://www.magesblog.com/2012/01/feedback-from-vignette-survey.html)

- [Syntax highlighting in  markdown](https://support.codebasehq.com/articles/tips-tricks/syntax-highlighting-in-markdown)

- [Rmarkdown - other language engines](http://yihui.name/knitr/demo/engines/)

- [Markdown syntax](http://sourceforge.net/p/pgbarman/tickets/markdown_syntax#md_ex_text)

- [Syntax highlighting in markdown](https://support.codebasehq.com/articles/tips-tricks/syntax-highlighting-in-markdown)

- [Get code from Rmarkdown](http://stackoverflow.com/questions/18884941/how-to-extract-r-code-from-a-markdown-file-md)

```{r,eval=F}
library(knitr)
purl("/Readme.md")
```



## Rpresentations

- [Rpresentations](http://stackoverflow.com/questions/23619319/rpresentation-in-rstudio-make-image-fill-out-the-whole-screen)

- [Presentations with Rmarkdown](http://rpubs.com/mansun_kuo/24330)


## Cite r-package `cluster`

```{r,cache=T}
citation(package = "cluster")
```

## Cite r-package `xlsx`

```{r}
citation(package = "xlsx")
```

## Cite r-package `foreign`

```{r}
citation(package = "foreign")
```

## Cite r-package `mice`

```{r,eval=F}
citation(package = "mice")
```

- [Citations in Rmarkdown](https://cran.r-project.org/web/packages/RefManageR/vignettes/TestRmd.html)


<http://www.blopig.com/blog/2013/07/citing-r-packages-in-your-thesispaperassignments/>

## Rstudio and git

[Rstudio shortcuts](https://support.rstudio.com/hc/en-us/articles/200711853-Keyboard-Shortcuts)

[Rstudio and git](http://www.r-bloggers.com/rstudio-and-github/)

[Github](https://github.com/jennybc/2015-06-28_r-summit-talk/blob/master/2015-06-28_bryan-r-summit-talk.pdf)

[Github 2](http://www.r-bloggers.com/get-by-with-a-little-r-help-from-your-friends-at-github/)

[education and github](http://blog.revolutionanalytics.com/2015/06/get-your-r-education-going-with-github.html)

## What's new on R

Get [news messages](http://cran.r-project.org/src/base/NEWS) about R. 

[Teaching with R](http://gastonsanchez.com/teaching/)

## Creating Shiny Apps

- [Hosting an App](http://shiny.rstudio.com/articles/deployment-local.html)

```{r,eval=F}
shiny::runGitHub('shiny_example', 'rstudio')


shiny::runGitHub(repo='ShinyApps', username='Japhilko',
                 subdir='EurostatMapApp/')
```

- [Shiny dashboard](https://rstudio.github.io/shinydashboard/get_started.html)

- [Shiny conference](http://www.eventbrite.com/e/shiny-developer-conference-registration-19153967031)

## Further links

- [formatR](https://cran.r-project.org/web/packages/formatR/index.html)

- [Portrait Ihaka](http://www.r-bloggers.com/ross-ihaka-co-creator-of-r-in-the-economist/)

- [Notebook for R](http://www.r-bloggers.com/interactive-data-science-with-r-in-apache-zeppelin-notebook/)

## Working with github

[clean git](http://stackoverflow.com/questions/52704/how-do-you-discard-unstaged-changes-in-git)

```
git clean - df
```