---
title: "Regression"
author: "Jan-Philipp Kolb"
date: "26 Juli 2016"
output:
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = F,warning=F)
library(knitr)
```

## [Linear Model](https://www.youtube.com/watch?v=5ONFqIk3RFg)

The following is based on course by Trevor Hastie and Rob Tibshirani on statistical learning.  

```{r,eval=F}
install.packages("ISLR")
```

```{r}
library("MASS")
library("ISLR")
```

```{r}
names(Boston)
# ?Boston
```

```{r fitlinearmodel}
plot(medv~lstat,Boston)
fit1 <- lm(medv~lstat,Boston)
summary(fit1)
```

[Picture - Simple Linear Regression](http://i0.wp.com/3.bp.blogspot.com/-M-eh1oV6NT0/Vn4nPWRl-LI/AAAAAAAAAbA/qiLz64Ky2Zw/s320/regression.png?resize=350%2C200)


```{r}
plot(medv~lstat,Boston)
abline(fit1,col=c("#8B008B"))
```

```{r}
confint(fit1)
predict(fit1,data.frame(lstat=c(5,10,15)),interval="confidence")
```

```{r}
fit2 <- lm(medv~lstat+age,Boston)
summary(fit2)
fit3 <- lm(medv~.,Boston)
summary(fit3)
```

```{r}
par(mfrow=c(2,2))
plot(fit3)
```

First plot: residuals vs fitted

is there some non-linearity - or straight line

Third plot: Scale Location

is the variance changing with the mean

```{r}
fit4 <- update(fit3,~.-age-indus)
summary(fit4)
```

## Model Selection

[Quick R - Multiple Regression](http://www.statmethods.net/stats/regression.html)

```{r}
library(MASS)
fit <- lm(medv~.,data=Boston)
step <- stepAIC(fit, direction="both")
step$anova # display results 
```

```{r}
library(relaimpo)
calc.relimp(fit,type=c("lmg","last","first","pratt"),
   rela=TRUE)
```



## Interactions

[with * the coefficients are used and also the interaction between them](http://www.gardenersown.co.uk/education/lectures/r/regression.htm)


```{r}
fit5 <- lm(medv~lstat*age,Boston)
summary(fit5)
```

```{r}
fit6 <- lm(medv ~ lstat +I(lstat^2),Boston)
summary(fit6)
attach(Boston)

plot(medv~lstat)
points(lstat,fitted(fit6),col="red",pch=20)

```

## Fitting Polynomials

```{r}
fit7 <- lm(medv ~ lstat +poly(lstat,4),Boston)
plot(medv~lstat)
points(lstat,fitted(fit7),col="blue",pch=20)
```

tends to overfit

```{r}
kable(head(Carseats))
```

```{r}
attach(Carseats)
mod1 <- lm(Sales~.+Income:Advertising,Carseats)
contrasts(ShelveLoc)
```

## Resources

- Faraway - [Practical Regression and Anova using R](https://cran.r-project.org/doc/contrib/Faraway-PRA.pdf)

- Breheny/Burchett - [Visualization of Regression Models Using visreg](http://myweb.uiowa.edu/pbreheny/publications/visreg.pdf)

- Wheeler - [Visualizing and Diagnosing Output from 
Geographically Weighted Regression Models](https://www.sph.emory.edu/departments/bios/documents/techdocs/2008/Tech_Report_08-02.pdf)