---
title: "Empirical Data Analysis"
author: "Jan-Philipp Kolb"
date: "24 August 2016"
output:
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=F,warning=F)
```

## Introduction

- [Spotty Statistics](http://www.statlit.org/pdf/2011SchieldISI6up.pdf)


## Data

- [Austrian PUF data](http://www.statistik.at/web_de/services/mikrodaten_fuer_forschung_und_lehre/kostenloser_download_von_testdaten/index.html)

- [Regional data RLP](http://www.statistik.rlp.de/regionaldaten/meine-heimat/)

- [Mietspiegel Munich](http://www.statistik.lmu.de/service/datenarchiv/miete/miete03.html)

## Tests

```{r}
N <- 1000
INC <- runif(N)
SEX <- sample(c(1,2),N,replace=T)

t.test(INC[SEX==1],INC[SEX==2])
```

- high p-value - we cannot reject the null hypothesis

## Regression with categorical y-variable

```{r,eval=F,echo=F}
install.packages("faraway")
```


```{r}
library(faraway)
data(orings)
plot(damage/6 ~ temp, orings, xlim=c(0,100), ylim=c(0,1),
    xlab="Temperatur", ylab="Unfall")
lmod <- lm(damage/6 ~ temp, orings)
abline(lmod, col=4); abline(h=0); abline(h=1)
```


```{r}
summary(m<-lm ( am ~ hp + wt,data=mtcars))
predict(m,data.frame(hp=65,wt=2))
predict(m,data.frame(hp=180,wt=2))
```


## Galapagos Example

```{r}
library(faraway)
data(gala)
gala<-gala[,-2]
gala$Species <- round(sqrt(gala$Species))
head(gala)
```


```{r,eval=F,echo=F}
install.packages("solaR")
```


```{r}
 library(solaR)
 splom(gala[,c(1,2,3,4)])
```

```{r}
summary(mod1<-lm(sqrt(Species)~Area+Elevation+Nearest,gala))
```

```{r}
predict(mod1,data.frame(Area = 200000,Elevation=40,Nearest=8))
```

[Information about binary data](http://stat.ethz.ch/education/semesters/WS_2005_06/asr/folien.pdf)


## Goodness-of-fit

```{r}
summary(glm(am ~ hp + wt, data=mtcars,family=binomial) )
```

## Multinomial Regression

```{r}
library(MASS)
example(birthwt)

head(bwt)

summary(bwt)
```

```{r}
library(nnet)

multinom(formula = low ~ ., data = bwt)
```

## Election Example

```{r}
head(nes96[,c(8:10)])
data(nes96)
sPID <- nes96$PID

summary(sPID)

levels(sPID) <- c("Democrat","Democrat","Independent",
"Independent", "Independent","Republican","Republican")

summary(sPID)

inca <- c(1.5,4,6,8,9.5,10.5,11.5,12.5,13.5,14.5,16,18.5,
  21,23.5,27.5,32.5,37.5,42.5,47.5,55,67.5,82.5,97.5,115)
 nincome <- inca[unclass(nes96$income)]
 summary(nincome)
 barplot(table(nes96$educ),col="chocolate1")
```

```{r}
matplot(prop.table(table(nes96$educ,sPID),1),type="l",
xlab="Education",ylab="Proportion",lty=c(1,2,5))
```

```{r}
library(nnet)
mmod <- multinom(sPID ~ age + educ + nincome, nes96)
 mmodi <- step(mmod)
```

## [Prediction](http://www.dartmouth.edu/~chance/teaching_aids/books_articles/probability_book/Chapters1-12.pdf)

```{r,eval=T}
il <- 5
 predict(mmodi,data.frame(nincome=il),type="probs")
summary(mmodi)
predict(mmodi,data.frame(nincome=0),type="probs")
```

We can see more explicitly what this means by predicting probabilities for incomes 1000 Dollar apart and then computing the log-odds:

```{r}
(pp <-
predict(mmodi,data.frame(nincome=c(0,1)),type="probs"))
```

- Akaike-Information criteria (AIC)
- Wald-Test
- Likelihood-Ratio-Test


##  Ordinal Regression

- Ordered response model
- Latent variable in ordered response model
- Proportional odds logistic regression (polr)

```{r}
library(MASS)
?polr
pomod <- polr(sPID ~ age + educ + nincome, nes96)
c(deviance(pomod), pomod$edf)
  
pomodi <- step(pomod)
summary(pomodi)
ilogit(0.209)
ilogit(1.292)-ilogit(0.209)
predict(pomodi,data.frame(nincome=il,row.names=il),  type="probs")
```

## Applied Econometrics with R (AER)

```{r,eval=F}
install.packages("AER")
```


```{r}
data("BankWages", package="AER")

summary(BankWages)
```

```{r}
library(lattice)
bwplot(BankWages$job ~BankWages$education | 
  BankWages$minority)
bwplot(BankWages$job ~BankWages$education | 
  BankWages$minority + BankWages$gender)
```

```{r}
tab <- table(BankWages$job, BankWages$education)
```

```{r,eval=F}
install.packages("gplots")
```



```{r}

library(gplots)
  balloonplot(BankWages$job, BankWages$education,
  BankWages$gender, xlab="job", ylab ="education")
```

```{r}
summary(polr(job ~ education + minority, data = BankWages,Hess = TRUE))
ilogit(mod1$zeta[1])
predict(mod1,BankWages[1:10,2:4],type="probs")
```

```{r}
library(faraway)
data(bliss)
bliss
modl <- glm(cbind(dead,alive) ~ conc, family=binomial, bliss)
residuals(modl)
 residuals(modl,"pearson")
 residuals(modl,"response")
  bliss$dead/30 - fitted(modl)
```

## Count Variables

```{r}
data(gala)
gala <- gala[,-2]
mod1 <- lm(Species ~ . , gala)
 modt <- lm(sqrt(Species) ~ . , gala)
 modp <- glm(Species ~ .,family=poisson, gala)
summary(modp)
```

## Examples for Half Normal Plots

[Answers to selected exercises](http://www.aliquote.org/articles/tech/RMB/c6_sols/RMB_c6_sols.html)

[Half-normal probability plot](http://itl.nist.gov/div898/handbook/pri/section5/pri598.htm)


## Cross Tabulation

```{r}
data(dicentric)
round(xtabs(ca/cells ~ doseamt + doserate,dicentric),2)

plot(residuals(lmod) ~ fitted(lmod),xlab="Fitted",
  ylab="Residuals")
abline(h=0)
```

```{r}
dicentric$dosef <- factor(dicentric$doseamt)
pmod <- glm(ca ~ log(cells)+log(doserate)*dosef,family=poisson,dicentric)
summary(pmod)
```

```{r}
rmod <- glm(ca ~ offset(log(cells))+log(doserate)*doseamt,
  family=poisson,dicentric)
summary(rmod)
```

## Visualising Categorical Data

```{r,eval=F}
install.packages("vcd")
```



```{r}
library(vcd)
data(nes96) 
sPID <- nes96$PID
levels(sPID) <- c("Democrat","Democrat","Independent",
"Independent","Independent","Republican","Republican")
Age <- nes96$age
cd_plot(sPID ~ Age)
```

## [Assurances Dataset](http://www.statsci.org/data/general/motorins.txt)

```{r}
motorins <- read.table("http://www.statsci.org/data/general/motorins.txt",header=T)
head(motorins)
attach(motorins)
```

```{r}
library(vcd)
distplot(Claims)
  assoc(table(Bonus,Make),shade=T,main="")
    cotabplot(~ Kilometres + Zone | Bonus, data = motorins)
```

## Anova

```{r}
x <- c(3,5,8,7,9,12,17,10,5,9,14,22)
y <- c(17,25,9,21,12,14,10,12,14,10,16,12,19,14,28)
```

```{r}
t.test(x, y, alternative="two.sided", var.equal=F,
        paired=F, mu=0, conf.level=0.99)
```

```{r}
WiWi    <- c(37097 ,45617, 41115 ,32510, 35940, 38247, 33352,
        42367, 29564 ,34896)
Sozi    <- c(46109, 28399, 42363 ,32928, 36893, 41527, 41074,
        27341, 36904 ,36247)
Math    <- c(41527, 36891 ,35220, 43529, 34941, 41565, 52383,
        36348, 37014 ,37897)
Stat    <- c("N", "N", "N", "J", "J", "N", "J", "N", "J", "J", "N", "J", "N", "J", "J", "N", "N", "J", "J",
"J", "N", "J", "J", "N", "J", "N", "N", "J", "J", "J")
```

```{r}
Studis <- c(WiWi, Sozi ,Math)
Index <- as.factor(rep(1:3,c(10,10,10)))
levels(Index) <- c("WiWi", "Sozi", "Math")
Data <- data.frame(Index=factor(Index),Studis,Stat)

boxplot(Studis ~ Index, col=c(2,3,4)); abline(h=mean(Studis), lty=2)

lines(c(0.55,1.45), c(mean(WiWi),mean(WiWi)), type="o")
lines(c(1.55,2.45), c(mean(Sozi),mean(Sozi)), type="o")
lines(c(2.55,3.45), c(mean(Math),mean(Math)), type="o")

summary(aov(Studis~Index,data=Data))
summary(aov(Studis~Stat,data=Data))
summary(aov(Studis~Index+Stat,data=Data))
summary(aov(Studis~Index*Stat,data=Data))
```

## Correspondence Analysis

```{r}
sex <- rep(1,100)
sex[sample(1:100,50)] <- 2

smog <- rep(1,100)
smog[sample(which(sex==1),20)]<- 2
smog[sample(which(sex==2),24)]<- 2

kont <- cbind(smog,sex)
kont1 <- table(smog,sex)


kont2<-ftable(sex~smog,data=kont)
kont2

chi <- chisq.test(kont1)

chi$expected

mu_e <- kont1

mu_e[1,1] <- prop.table(colSums(kont1))[1]*prop.table(rowSums(kont1))[1]
mu_e[1,2] <- prop.table(colSums(kont1))[1]*prop.table(rowSums(kont1))[2]
mu_e[2,1] <- prop.table(colSums(kont1))[2]*prop.table(rowSums(kont1))[1]
mu_e[2,2] <- prop.table(colSums(kont1))[2]*prop.table(rowSums(kont1))[2]


sum(((prop.table(kont1) - mu_e)^2) /mu_e)
```

## FactoMineR

```{r,eval=F}
install.packages("FactoMineR")
```


```{r}
library(FactoMineR)
data(children)

which(names(children)=="high_school_diploma")
which(names(children)=="university")
which(names(children)=="more_fifty")


names(children)[4] <- "dipl"
names(children)[5] <- "uni"
names(children)[1] <- "unqual"
names(children)[8] <- "m50"
names(children)[7] <- "50"
names(children)[6] <- "30"

```

