---
title: "Graphical Analysis"
author: "Jan-Philipp Kolb"
date: "20 Oktober 2016"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## [Plotting Confidence Intervals](http://stackoverflow.com/questions/14069629/plotting-confidence-intervals)

```{r,eval=F}
install.packages("plotrix")
```



```{r}
# install.packages("plotrix")
library(plotrix)
set.seed(0815)
x <- 1:10
F <- runif(10,1,2) 
L <- runif(10,0,1)
U <- runif(10,2,3)

require(plotrix)
plotCI(x, F, ui=U, li=L)
```

## [Plotting Time Series](https://cran.r-project.org/web/packages/timeSeries/vignettes/timeSeriesPlot.pdf)

```{r}
# install.packages("timeSeries")
library(timeSeries)
```

```{r}
tS1 <- 100 * cumulated(LPP2005REC[, 1]) # SBI (univariate)
tS2 <- 100 * cumulated(LPP2005REC[, 1:2]) # SBI & SPI (bivariate)
tS3 <- 100 * cumulated(LPP2005REC[, 1:3]) # SBI, SPI, SWIIT (Swiss Market)
tS6 <- 100 * cumulated(LPP2005REC[, 1:6]) # Swiss and Foreign Market Indexes
5
```

```{r}
par(mfrow=c(1, 1))
plot(tS3, plot.type="s")
```


## Visualizing Categorical Data

- [Working with categorical data with R and the vcd and vcdExtra packages](https://cran.r-project.org/web/packages/vcdExtra/vignettes/vcd-tutorial.pdf)

- New Approaches in Visualization of Categorical Data: R Package extracat

## Misc 

- [Legends in Base Graphics](http://stackoverflow.com/questions/3932038/plot-a-legend-outside-of-the-plotting-area-in-base-graphics)

```{r}
set.seed(121)
a=sample(1:100,5)
b=sample(1:100,5)
c=sample(1:100,5)

layout(rbind(1,2), heights=c(7,1))  # put legend on bottom 1/8th of the chart

plot(a,type='l',ylim=c(min(c(a,b,c)),max(c(a,b,c))))
lines(b,lty=2)
lines(c,lty=3,col='blue')

# setup for no margins on the legend
par(mar=c(0, 0, 0, 0))
# c(bottom, left, top, right)
plot.new()
legend('center','groups',c("A","B","C"), lty = c(1,2,3),
       col=c('black','black','blue'),ncol=3,bty ="n")
```


## [Producing a line plot with `ggplot2`](http://www.sthda.com/english/wiki/ggplot2-line-types-how-to-change-line-types-of-a-graph-in-r-software)


```{r}
df2 <- data.frame(sex = rep(c("Female", "Male"), each=3),
                  time=c("breakfeast", "Lunch", "Dinner"),
                  bill=c(10, 30, 15, 13, 40, 17) )
head(df2)
```


```{r}
ggplot(df2, aes(x=time, y=bill, group=sex)) +
  geom_line(aes(linetype=sex, color=sex))+
  geom_point(aes(color=sex))+
  theme(legend.position="top")
```

- [Size of axis labels](http://stackoverflow.com/questions/14942681/change-size-of-axes-title-and-labels-in-ggplot2)


## Resources

- [Computing and visualizing PCA in R](https://www.r-bloggers.com/computing-and-visualizing-pca-in-r/)

- [Alternatives for boxplots](http://www.sthda.com/english/wiki/ggplot2-easy-way-to-mix-multiple-graphs-on-the-same-page-r-software-and-data-visualization)