---
title: "Miscelaneous"
author: "Jan-Philipp Kolb"
date: "27. Juli 2015"
output: ioslides_presentation
---

## Data science

- [Data scientist](http://www.r-bloggers.com/oreilly-data-scientist-salary-and-tools-survey-november-2014/)



## Java

- [JRI - Java/R Interface](http://rforge.net/JRI/index.html)

```{r,eval=F}
system.file("jri",package="rJava")
```

<http://clojure.org/>

## Google programming language GO

<https://golang.org/>


##  getting to know html

<https://developer.mozilla.org/en-US/docs/Web/Guide/HTML/Introduction>

## Javascript

<http://www.dateiendung.com/format/js>

<http://www.r-bloggers.com/introducing-v8-an-embedded-javascript-engine-for-r/>

- [Fiddles](http://jsfiddle.net/user/opencpu/fiddles/)

- Jeroen Ooms - [Introducing V8: An Embedded JavaScript Engine for R](https://www.opencpu.org/posts/v8-release-0-2/)
<https://www.r-bloggers.com/introducing-v8-an-embedded-javascript-engine-for-r/>

## R and Javascript

<http://www.r-bloggers.com/statistical-computation-in-javascript-am-i-nuts/>

<http://www.htmlwidgets.org/>

## Running javascript using V8


```{r,eval=F}
# library(V8)
# data(diamonds, package="ggplot2")
# ct <- new_context()
# ct$assign("diamonds", diamonds)
# 
# # Load CrossFilter JavaScript library
# ct$source("http://cdnjs.cloudflare.com/ajax/libs/crossfilter/1.3.11/crossfilter.min.js")
# 
# ct$console()
```

## Some helpers

<http://www.w3schools.com/html/html_intro.asp>

## Open CPU

<https://www.opencpu.org/>

## Further Languages

Comparison of R and other statistical programs

<http://blog.datacamp.com/statistical-language-wars-the-infograph/>

<http://www.rzbt.haw-hamburg.de/dankert/ccppjava.html/>

## R and Hadoop

<https://github.com/RevolutionAnalytics/RHadoop/wiki>

```{r}
# http://rapache.net/
```

- [Step-by-Step Guide to Setting Up an R-Hadoop System](http://www.rdatamining.com/big-data/r-hadoop-setup-guide)

- [Tutorial RHadoop](http://hortonworks.com/hadoop-tutorial/using-rhadoop-to-predict-visitors-amount/)

## Using a database and R

<http://www.r-bloggers.com/using-azure-as-an-r-datasource-part-2-pulling-data-from-mysqlmariadb/>

## Links

<http://www.r-bloggers.com/become-an-effective-data-hacker-with-the-r-hadoop-stack/>
<http://blog.revolutionanalytics.com/2011/09/mapreduce-hadoop-r.html>


